\appendix

\section{Research Papers}\label{papers}

\textbf{Paper 1} Mora, S., Boron, A., \& Divitini, M. (2012). CroMAR:
Mobile Augmented Reality for Supporting Reflection on Crowd Management.
\emph{International Journal of Mobile Human Computer Interaction}, 4(2),
88--101. Available at: http://simonemora.me/papers/P1.pdf

\textbf{Paper 2} Mora, S., \& Divitini, M. (2014). Supporting Debriefing
with Sensor Data: A Reflective Approach to Crisis Training. \emph{In
Proceeding of Information Systems for Crisis Response and Management in
Mediterranean Countries, ISCRAM-MED}, 196(7), 71--84. Available at:
http://simonemora.me/papers/P2.pdf

\textbf{Paper 3} Mora, S., \& Divitini, M. (2014). WATCHiT: a modular
and wearable tool for data collection in crisis management and training.
\emph{In Proceeding of the European Conference in Ambient Intelligence,
AMI}, 8850(22), 274-289. Available at:
http://simonemora.me/papers/P3.pdf

\textbf{Paper 4} Di Loreto, I., Mora, S., \& Divitini, M. (2012). Don't
Panic: Enhancing Soft Skills for Civil Protection Workers. \emph{In
Proceeding of International Conference on Serious Games Development
Applications, SGDA}, 7528(1), 1--12. Available at:
http://simonemora.me/papers/P4.pdf

\textbf{Paper 5} Mora, S., Di Loreto, I., \& Divitini, M. The
interactive-token approach to board games. \emph{Ready for submission}.
Available at: http://simonemora.me/papers/P5.pdf

\textbf{Paper 6} Müller, L., Divitini, M., Mora, S., Rivera-Pelayo, V.,
\& Stork, W. (2014). Context Becomes Content: Sensor Data for Computer
Supported Reflective Learning. \emph{IEEE Transactions on Learning
Technologies}, PP(99). Available at: http://simonemora.me/papers/P6.pdf

\textbf{Paper 7} Mora, S., \& Farshchian, B. A. (2010). A Unified
Architecture for Supporting Direct Tag-Based and Indirect Network-Based
Resource Discovery. \emph{In Proceeding of the International Conference
on Ambient Intelligence, AMI}, 6439(20), 197--206. Available at:
http://simonemora.me/papers/P7.pdf
