\chapter{Acknowledgments}
\enlargethispage{\baselineskip}

Foremost, I would like to express my deepest gratitude to my supervisor Professor Monica Divitini and co-advisor Associate Professor Babak Farshchian. Your guidance and precious advices made me a better researcher and a better person. Your support and trust, always present throughout my PhD journey, make me proud. You have been an example for me, I cannot think of better supervisors to have.

I wish to thank former and current colleagues that have contributed in many ways to my work: Birgit, Ines and Alessandro for co-authoring some of the papers, Emanuele for helping with the prototyping work; my officemates Elena, Francesco and Hans for the coffee-breaks. 

I extend my gratitude to other members of the Department of Computer and Information Science for their opinions and insights; and the staff of NTNU Technology Transfer AS, in particular Marit, Silje and Kjetil, for bringing their perspective and ideas into my research. I also thank Stewart Clark for editing Part I of this thesis.

Taking part to the MIRROR project has been essential to achieve the research goals reported in this thesis. I thank all the consortium members for the productive discussions, especially Regola s.r.l and Mr.\ Gianni della Valle for arranging the field studies this research work builds on.

During part of my PhD training I was honoured to be a guest in two foreign institutions. I thank Professor Neil Maiden at the City London University for his supervision, and colleagues and friends Anja, for the teamwork; Dara, Graham, Milena, Minou, Mobina and Jacques for taking part to the evaluation of prototypes. I'm grateful to Professor Carlo Ratti at the MIT SENSEable City Lab for his lead; and colleagues and friends Professor Paolo Santi, Professor Rex Britter, Aldo, Alice, Anthony, Chris, Clara, Kris, Luis, Matteo, Matthew, Miriam, Newsha, Pierrick, Ricardo, Remi and Yuji for their amazing work.    

I am indebted to all my friends who have supported me over the last few years, those here in Norway and those in Italy. Thanks for being always there for me.

Finally, I want to express my affection to my awesome family: Lucia, Mario, Martina and Stefano, Antonella, Corrado and Federica; grandparents Benedetta and Costante. Without you all of this would not have been possible, \emph{thanks}.

\begin{flushright}
\emph{\small Simone Mora}\\\emph{\small February 26th, 2015}	
\end{flushright}


