\documentclass{article}[10pt]
\usepackage{longtable}
\usepackage{lscape}

\begin{document}

\begin{landscape}
\begin{longtable}{p{2cm}p{3cm}p{3cm}p{3cm}p{4cm}p{1cm}p{1cm}}
ID(*=key study) & Date, duration   & Setting  & Participants  & Research Methods \newline Research Activity & RQs & Research Papers \\ 
\hline
1(*)   & March 2011, 2 days     & Real work   & several teams    & Observations, interviews User study.  & 2   & P1  \\
2(*) & October 2011, 3 days   & Simulated work in a maxi emergency & several teams, 1 manager     & Observations, interviews, video analysis. Formative evaluation of CroMAR v01. & 2   & P1 \\
3  & April 2012, 1 day      & Focus group    & 9 field workers, 1 manager   & Interviews. Evaluation of WATCHiT v01 and Don't Panic paper mockup. & 1-2 & P3-P5     \\
4  & May 2012, 1 day        & Focus group      & 1 manager     & Observation, Interview. Formative evaluation of WATCHiT v02 and CroMAR v02  & 1-2 & P1-P3           \\
5(*) & October 2012, 2 days   & Simulated work    & 5 field workers, 1 manager   & Observation, interviews, video analysis. Formative Evaluation of WATCHiT v03 and CroMAR v02  & 1-2 & P1-P3   \\
6   & April 2013, 3 days     & Simulated work in a maxi emergency & 4 field workers, 1 manager   & Observation, interviews, video analysis, questionnaires. Summative evaluation of CroMAR v02, formative evaluation of WATCHiT v03 & 1-2 & P1-P3    \\
7(*) & July 2013, 1 day       & Focus group    & 3 field workers, 1 manager   & Observations, interviews, video analysis, questionnaires. Formative evaluation of Don't Panic v01  & 2   & P4              \\
8      & September 2013, 1 day  & Focus group    & 8 IT students, 4 HCI experts & Observations, interviews, video analysis, questionnaires. Formative evaluation of Don't Panic v01    & 2   & P4     \\
9     & December 2013, 30 days & Simulated work      & 8 field workers      & Questionnaires Summative evaluation of WATCHiT v04      & 1   & P2-P3-P7        \\
10(*)  & April 2014, 2 days     & Simulated work       & 27 field workers, 1 manager  & Observations, Questionnaires Summative evaluation of WATCHiT v04    & 1   & P2-P3-P7  \\ 
\end{longtable}
\end{landscape}

\end{document}